Trauma treatment delay

### 2023-11-10 manuscriptlongversion.Rmd
text

We conducted a registry based cohort study using data from the trauma
registry and trauma care quality database at the Karolinska University
Hospital in Solna. The trauma registry includes about 11864 patients
treated between 2012 and 2022. The trauma care quality database is a
subset of the trauma registry and includes about 8000 patients selected
for review between 2013 and 2022. This project will link the two
databases and assess how different patient level factors, such as age,
sex, mechanism of injury, and injury severity, are associated with
delayed treatment using logistic regression.

@@

Multivariable and potentially univariable logistical regression. A 5%
significance level and 95% confidence levels will be used.

Rstudio was used to perform the logistical regression. The dependent
variable is OFI_delay, which is the presence of the ofi delayed
treatment.

@@

The 6,489 patients included in the study. 68% of the individuals
included were men, with the remaining 32% being women. The mean value
for the ISS score was 10.49, with the standard deviation being 11.4. The
patients had a mean GCS of ... with a standard deviation of ...

>>>>

We conducted a registry based cohort study using data from the trauma
registry and trauma care quality database at the Karolinska University
Hospital in Solna. The trauma registry includes about 14,022 patients
treated between 2012 and 2022. The trauma care quality database is a
subset of the trauma registry and includes about 8000 patients selected
for review between 2013 and 2022. This project will link the two
databases and assess how different patient level factors, such as age,
sex, blood pressure, and injury severity, are associated with delayed
treatment using logistic regression.

@@

Multivariable and univariable logistical regression. A 5% significance
level and 95% confidence levels will be used.

Rstudio was used to perform the logistical regression. The code was
written to clean and prepare the data from the database. The data was
processed to have the variables customized to fit into the logistical
regression model.

For the missing hospital values in GCS, RR and SBP, values from EMT
personnel were used

The dependent variable is OFI_delay, which is the presence of the ofi
delayed treatment.

@@

The 6,489 patients included in the study. 68% of the individuals
included were men, with the remaining 32% being women. The mean value
for the ISS score was 10.49, with the standard deviation being 11.4. The
patients had a mean GCS of ... with a standard deviation of ... The
majority of the patients had General care department as their highest
care level, followed by ICU, ER, OR and lastly specialized care
department. The mean respiratory rate in the overall group was ..., with
a standard deviation of ... The mean SBP was ..., having a standard
deviation of ... The majority of patients, 85%, were not intubated
during their stay in the hospital, followed by 9.1% intubated at the
hospital and 6% intubated prehospitaly. The mean age of the patients was
... years old, with a standard deviation of ... Most of the patients
arrived during on-call hours,..., with the rest arriving during working
hours. 67% of the patients arrived on a weekday, with the rest arriving
on the weekend.
